Joint analysis of read count data

### 2020-09-09 combined_analysis/combine_all_data.Rmd
add zenith

# SCZ by sex
# L_SCZ = Lbase
# L_SCZ['DxSCZ:Reported_GenderMale'] = 1
# L_SCZ['DxControl:Reported_GenderMale'] = -1
# L_SCZ['DxSCZ'] = -1
# L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

# # BP by sex
# L_BP = Lbase
# L_BP['DxBP:Reported_GenderMale'] = 1
# L_BP['Reported_GenderMale'] = -1
# L_BP['DxBP'] = -1
# L_BP['DxControl'] = 1

@@

>>>>

@@

browser()
